Matching Bullets

### 2015-11-24 imaging-paper.Rnw
added a couple of references

Rough outline:
\begin{enumerate}
\item Description of the problem: Standard operating practice, 2009 NAS report
\item Description of the Results
\item Walkthrough of the process
\item \hh{XXX Alternative approaches: IBIS database and the NRC report against it\footnote{Fox report on the NRC report \url{http://goo.gl/XurSVl}.
NRC report: \url{http://www.nap.edu/catalog/12162/ballistic-imaging}} }
\end{enumerate}

@@

The new scrutiny of the procedure culminated with the 2009 National Academy of Sciences report \cite{NAS:2009}. The report concluded that minimal research had been done exploring the reliability of these ballistic identification methods. In fact, the report says the forensic evidence ``including, for example, bite marks and rearm and toolmark identification is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline."

@@

Rifling in the barrel creates striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel, as described in a 1992 AFTE article. ``The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in sufficient agreement" The article goes on to state that ``Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows." \footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}, \footnote{AFTE 1992 theory of identification \url{http://projects.nfstc.org/firearms/module09/fir_m09_t05_05.htm}}

@@

\hh{Figure~\ref{fig:match} gives an overview of the rest of the automated matching routine: after smoothing the scan with a loess of a very small span, shown in (a), we define a striation mark as a groove or a peak if it exceeds a pre-set threshold (of 0.75$\mu m$; obviously this is a crucial parameter. For more discussion see Figure~\ref{fig:thresholds}). Two lines are defined as a match, if their peak/groove base at the threshold overlaps. If there is no overlap, a peak/groove leads to a mismatch. We then count the number of maximum consecutive matches. In this example, the number of consecutive matching striations (CMS) is fifteen, a very high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti \cite{biasotti:1959} XXX need more references XXX considered four or more consecutive lines to be sufficient evidence of a match. }

>>>>

Rough outline:
\begin{enumerate}
\item Description of the problem: Standard operating practice, 2009 NAS report
\item Description of the Results
\item Walkthrough of the process
\item \hh{XXX Alternative approaches: IBIS database and the NRC report\cite{nap:2008} against it\footnote{Fox report on the NRC report \url{http://goo.gl/XurSVl}.
NRC report: \url{http://www.nap.edu/catalog/12162/ballistic-imaging}} }
\end{enumerate}

@@

The new scrutiny of the procedure culminated with the 2009 National Academy of Sciences report \cite{NAS:2009}. The report concluded that minimal research had been done exploring the reliability of these ballistic identification methods. In fact, the report says the forensic evidence ``including, for example, bite marks and firearm and toolmark identification is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline."

@@

Rifling in the barrel creates striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel, as described in a 1992 AFTE article \cite{afte:1992}. ``The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in sufficient agreement" The article goes on to state that ``Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows." \footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}, \footnote{AFTE 1992 theory of identification \url{http://projects.nfstc.org/firearms/module09/fir_m09_t05_05.htm}}

@@

\hh{Figure~\ref{fig:match} gives an overview of the rest of the automated matching routine: after smoothing the scan with a loess of a very small span, shown in (a), we define a striation mark as a groove or a peak if it exceeds a pre-set threshold (of 0.75$\mu m$; obviously this is a crucial parameter. For more discussion see Figure~\ref{fig:thresholds}). Two lines are defined as a match, if their peak/groove base at the threshold overlaps. If there is no overlap, a peak/groove leads to a mismatch. We then count the number of maximum consecutive matches. In this example, the number of consecutive matching striations (CMS) is fifteen, a very high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti \cite{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match. XXX need more references XXX \cite{nichols:2003} XXX what does the paper say? AFTE is so frustrating! XXX }
